Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-01-29 xrb2/paper.tex
tangential -> perpendicular

We present six simulations in total, summarized in
Table~\ref{table:runs}.  These simulations encompass three different
rotation rates: $250~\mathrm{Hz}$, $500~\mathrm{Hz}$, and $1000~\mathrm{Hz}$, 
and for the $500~\mathrm{Hz}$ run, four
different temperature profiles.  In the following subsections, we look
at how the flame properties depend on the model parameters.  All
simulations are run in a domain of $1.8432\times 10^5~\mathrm{cm} \times
3.072\times 10^4~\mathrm{cm}$ with a coarse grid of $1152 \times 192$
zones and two levels of refinement (the first level refining the resolution 
by factor of four, and the second by a factor of two again).  This gives a
fine-grid resolution of $20~\mathrm{cm}$.  In these simulations, refinement 
is carried out in all zones within the atmosphere
with density $\rho > 2.5\times 10^4~\gcc$. We use an axisymmetric coordinate system, 
with the horizontal $r$-direction pointing along the surface of the star and the 
vertical $z$-direction pointing tangential to the surface.

>>>>

We present six simulations in total, summarized in
Table~\ref{table:runs}.  These simulations encompass three different
rotation rates: $250~\mathrm{Hz}$, $500~\mathrm{Hz}$, and $1000~\mathrm{Hz}$, 
and for the $500~\mathrm{Hz}$ run, four
different temperature profiles.  In the following subsections, we look
at how the flame properties depend on the model parameters.  All
simulations are run in a domain of $1.8432\times 10^5~\mathrm{cm} \times
3.072\times 10^4~\mathrm{cm}$ with a coarse grid of $1152 \times 192$
zones and two levels of refinement (the first level refining the resolution 
by factor of four, and the second by a factor of two again).  This gives a
fine-grid resolution of $20~\mathrm{cm}$.  In these simulations, refinement 
is carried out in all zones within the atmosphere
with density $\rho > 2.5\times 10^4~\gcc$. We use an axisymmetric coordinate system, 
with the horizontal $r$-direction pointing along the surface of the star and the 
vertical $z$-direction pointing perpendicular to the surface.
